SoK: Application Attack Defenses (in Question)

### 2014-09-23 docs/questioning.tex
new title (SoK is a mandatory prefix)
we need to define our terms

\title{Questioning how Researchers Present Intrusion Detection Systems}

\maketitle
\begin{abstract}
In this paper we examine how intrusion-detection
systems developed to counter a specific category
of application attacks are developed and presented to
the research community.
\end{abstract}

\begin{IEEEkeywords}
Security and Protection, Intrusion-Detection Systems, Code injection Attacks, Cyber Security Experiments, Effectivenes, Efficiency.
\end{IEEEkeywords}

@@

\section{Intrusion Detection Accuracy}

>>>>

\title{SoK: Application Attack Defenses (in Question)}

\maketitle
\begin{abstract}
In this paper we examine how application attack defense
mechanism are developed and presented to
the research community.
\end{abstract}

\begin{IEEEkeywords}
Security and Protection, Application Security, Code injection Attacks, Cyber Security Experiments, Effectivenes, Efficiency.
\end{IEEEkeywords}

@@

\section{Application Attack Defense Mechanisms Accuracy}
% @Panos: we need to change our terminology. Instead of intrusion-detection
% systems we need to move to something like application attack defences.
% Intrusion detection is very broad and we are currently
% surveying mechanisms that detect attacks coming from a specific catefory.
